Data analysis to support temporary cycleways

### 2020-05-06 README.Rmd
Update with definition of cycling potential

The results are not intended to be a definitive list of places where pop-up cycleways should be prioritised.
There may be 'false positives' where there are strong reasons for not converting a 'spare lane' into a cycleway or temporary pavement.
There will be many road sections that would benefit from interventions not shown in the maps below: for example roads with only one lane in each direction could be made oneway temporarily, creating a spare lane for cycleways or extra pavement width.

<!-- We filtered-out roads with low levels of cycling potential and focus only on roads that have at least one 'spare lane', defined as having more than 1 lane in either direction. -->
Such roads and roads that could be converted into 'liveable streets' by preventing through traffic have not been considered at this stage.
Providing evidence to identify such roads, e.g. where there is high demand but little road width, suggesting a strong argument for making them one-way during a period of vital physical distancing, in addition to the roads with 'spare lanes' identified below, could be an aim of future work.

@@

The results below show all roads with a 'spare lane' in the low average traffic conditions created by the partial lockdown (light blue) based on the three criteria listed above (lanes, potential and length) plus the top 10 roads of a minimum length in terms of estimated cycling potential under the Government Target scenario in the PCT (dark blue).

>>>>

The results are not a definitive list of places where pop-up cycleways should be prioritised but a 'starter for 10' highlighting roads that good candidates for 'pop-up' active transport infrastructure through reallocation of road space, as has happened in [Park Lane in London](https://www.forbes.com/sites/carltonreid/2020/05/06/pop-up-cycleway-for-park-lane-as-tenfold-increase-in-cycling-predicted-for-london/#48aad0705b1e).
The results highlight roads that have cycling potential and at least one spare lane, meaning a 2 lanes in one direction.
There will be many road sections that would benefit from interventions not shown in the maps below: for example roads with only one lane in each direction could be made oneway temporarily, creating a spare lane for cycleways or extra pavement width.
Prevent through-flow in residential areas, as is happening in [Lewisham](https://853.london/2020/05/05/lewisham-council-asks-which-streets-it-should-open-up-to-walkers-and-cyclists/) is another option that can complement road reallocation.

<!-- We filtered-out roads with low levels of cycling potential and focus only on roads that have at least one 'spare lane', defined as having more than 1 lane in either direction. -->
<!-- Such roads that could be converted into 'liveable streets' by preventing through traffic have not been considered at this stage. -->
Evidence supporting other types of interventions, for example where there is high demand for access to key workplaces but little space for walking and cycling, could be an aim of future work.

@@

The results below show all roads with a 'spare lane' in **light blue** based on the three criteria listed above (lanes, potential and length).
The top 10 roads in terms of cycling potential are shown in **dark blue**.
Cycling potential refers to the number of commuters who would cycle along the road (either to or from work) under the Government Target based on data from the Department for Transport funded Propensity to Cycle Tool (see [www.pct.bike](https://www.pct.bike/)).
